# Going further


## I want to dig deeper

Check-out my [intro stats book](https://statistik1.netlify.app/) to get an overview on statistical modeling using  regression techniques. Please use your browser's translation feature to render the webpages into your favorite language.


Check-out this [course on statistical inference using Bayes statistics](https://start-bayes.netlify.app/).
If you are interested in predictive modeling, check-out [this course](https://ds1-prognosemodellierung.netlify.app/).


## More exercises

There's a ton of exercises available at the [Datenwerk](https://datenwerk.netlify.app/).


## Case studies



### Case studies on data visualization


```{r child-vis, results='asis', echo = FALSE}
url <- "https://raw.githubusercontent.com/sebastiansauer/Lehre/main/Material/yacsdas-vis.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```








### Case studies on explorative data analysis


```{r child-eda, results='asis', echo = FALSE}
url <- "https://raw.githubusercontent.com/sebastiansauer/Lehre/main/Material/yacsdas-EDA.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```








## Case studies on linear models




```{r child2, results='asis', echo = FALSE}
url <- "https://raw.githubusercontent.com/sebastiansauer/Lehre/main/Material/yacsdas-lm.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```



### Case studies on machine learning using tidymodels



```{r child3, results='asis', echo = FALSE}
url <- "https://raw.githubusercontent.com/sebastiansauer/Lehre/main/Material/yacsdas-tidymodels.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```




## Recommened reading



Check-out the references pointed out in this course.

In addition, [here's a Zotero group with recommended resources on empirical research and statistical modeling](https://www.zotero.org/groups/4583286/intro-stats/library).
Note that the resources are of introductory nature.



## Have fun

And while we are talking about it, follow a strong purpose.

Best of luck!





